Analysis plan

### 2023-09-11 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd
Adding per month metrics and adjusting title placement and size in alluvial chart

```{r}
d <- 
  d %>% 
  mutate(across(
    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
    .fns = ~./prep_val_01,
    .names = "{col}_ppp"
  ))
```

@@

```{r}
d %>% 
  skim(ends_with("_ppp"))
```

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(daily_status_reporting_to_job_site,
       daily_status_reporting_to_job_site_observation_prop,
       daily_status_reporting_to_job_site_working_prop,
       daily_status_reporting_to_job_site_ppp,
       daily_status_teleworking,
       daily_status_teleworking_observation_prop,
       daily_status_teleworking_working_prop,
       daily_status_teleworking_ppp,
       days_colocated_1,
       days_colocated_1_observation_prop,
       days_colocated_supervisor,
       days_colocated_supervisor_observation_prop,
       days_colocated_team,
       days_colocated_team_observation_prop,
       days_telework_team,
       days_telework_team_observation_prop,
       working_days,
       team_size_mode)
```

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  summarise(
    across(
      .cols = c(daily_status_reporting_to_job_site_ppp,
                daily_status_reporting_to_job_site_working_prop,
                daily_status_teleworking_ppp,
                daily_status_teleworking_working_prop),
      .fns = list(q_025 = ~quantile(.,probs = .025),
                  q_975 = ~quantile(.,probs = .975))
    )
  ) %>% 
  pivot_longer(-.cluster_5) %>% 
  pivot_wider(values_from = value, names_from = .cluster_5)
```

@@

```{r}
p_2 <- 
  prep_d_05 %>% 
  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
  ggplot(aes(y = num, axis1 = position_category_description, axis2 = .cluster_5, fill = .cluster_5)) +
  geom_alluvium(width = 1/12) +
  geom_stratum(width = 1/12,
               # alpha = 1,
               fill = "black",
               color = "white"
               ) +
  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
             fill = "white",
             # , alpha = .05,
              size = 2,
             hjust = "inward"
             ) +
  labs(title = "Linking position categories to work pattern groups") +
  ylab("Number of employees") +
  scale_y_continuous(labels = scales::comma) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.y = element_text(size = 8),
    axis.title.x = element_blank(),
    axis.text.x = element_blank())
```

@@

```{r}
ggsave(filename = fp, plot = p_2, width = 6, height = 3, units = "in")
```
# Clusters: How much telework?

@@

>>>>

```{r}
d <- 
  d %>% 
  mutate(across(
    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
    .fns = list(ppp = ~./prep_val_01,pm = ~./params$observation_window_length_months),
    .names = "{col}_{fn}"
  ))
```

@@

```{r}
d %>% 
  skim(ends_with("_ppp"),ends_with("_pm"))
```

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(daily_status_reporting_to_job_site,
       daily_status_reporting_to_job_site_observation_prop,
       daily_status_reporting_to_job_site_working_prop,
       daily_status_reporting_to_job_site_ppp,
       daily_status_reporting_to_job_site_pm,
       daily_status_teleworking,
       daily_status_teleworking_observation_prop,
       daily_status_teleworking_working_prop,
       daily_status_teleworking_ppp,
       daily_status_teleworking_pm,
       days_colocated_1,
       days_colocated_1_observation_prop,
       days_colocated_supervisor,
       days_colocated_supervisor_observation_prop,
       days_colocated_team,
       days_colocated_team_observation_prop,
       days_telework_team,
       days_telework_team_observation_prop,
       working_days,
       team_size_mode)
```

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  summarise(
    across(
      .cols = c(daily_status_reporting_to_job_site_ppp,
                daily_status_reporting_to_job_site_pm,
                daily_status_reporting_to_job_site_working_prop,
                daily_status_teleworking_ppp,
                daily_status_teleworking_pm,
                daily_status_teleworking_working_prop),
      .fns = list(q_025 = ~quantile(.,probs = .025),
                  q_975 = ~quantile(.,probs = .975))
    )
  ) %>% 
  pivot_longer(-.cluster_5) %>% 
  pivot_wider(values_from = value, names_from = .cluster_5)
```

@@

```{r}
p_2 <- 
  prep_d_05 %>% 
  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
  ggplot(aes(y = num, axis1 = position_category_description, axis2 = .cluster_5, fill = .cluster_5)) +
  geom_alluvium(width = 1/12) +
  geom_stratum(width = 1/12,
               # alpha = 1,
               fill = "black",
               color = "white"
               ) +
  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
             fill = "white",
             # , alpha = .05,
              size = 2,
             hjust = "inward"
             ) +
  labs(title = "Linking position categories to work pattern groups") +
  ylab("Number of employees") +
  scale_y_continuous(labels = scales::comma) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "None",
    plot.title = element_text(hjust = 0.5,
                              size = 13),
    axis.title.y = element_text(size = 8),
    axis.title.x = element_blank(),
    axis.text.x = element_blank())
```

@@

```{r}
ggsave(filename = fp, plot = p_2, width = 6, height = 3, units = "in")
```

# Clusters: How much telework?

@@

# Difference in colocation

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(team_size_mode,starts_with("days_colocated"), starts_with("days_telework"))
```
